Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-13 papers/LREC2020/analysis.tex
solves a couple of issues and makes fit again

We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19. 
With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which shows names that have at least frequency 2.
The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
Hence, in our data, objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, but at the same time there is variation.

@@

To further assess agreement on the object names, we check the following measures, computed with \mbox{$t$=$2$}, with results in Table~\ref{tab:agree}:
\begin{itemize}
\item \textbf{N}: the average number of types in the response set. %of ManyNames.
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
\item $\mathbf{H}$: the $H$ agreement measure from \cite{snodgrass}, where $0$~is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$~denotes the number of name types and $p_i$~is the proportion of type~$i$ in the responses. 
\item \textbf{t=VG}: the percentage of items where the top response in ManyNames is the \vg name.
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
\end{itemize}

>>>>

We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19. 
With a reasonable threshold of $t$=2 (based on data inspection; names entered by one annotator only have the most noise, which is to be expected), a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
This threshold is used in Fig.~\ref{fig:ex-high-low-agreement}, showing names that have at least frequency 2.
The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
Hence, in our data, objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, but at the same time there is variation.

@@

To further assess agreement on the object names, we check the following measures, computed with \mbox{$t$=$2$}, with results in Table~\ref{tab:agree}:
\begin{itemize}
  \setlength\itemsep{-0.5pt}
\item \textbf{N}: the average number of types in the response set. %of ManyNames.
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
\item $\mathbf{H}$: the $H$ agreement measure from \cite{snodgrass}, where $0$~is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$~denotes the number of name types and $p_i$~is the proportion of type~$i$ in the responses. 
\item \textbf{t=VG}: the percentage of items where the top response in ManyNames is the \vg name.
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
\end{itemize}

### 2020-03-13 papers/LREC2020/data-collection.tex
fixes errors in Fig 3
solves a couple of issues and makes fit again

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{lp{14cm}}
			\toprule
			Domain & \multicolumn{1}{c}{Collection synsets}\\
			\midrule			
			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
			\bottomrule
		\end{tabular}
		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
                  \label{tab:overview_dataset2}}
	\end{table*}

@@

\begin{figure*}[htp]
	\centering
	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN.png}
	\caption{Cumulative histograms of the number of images and \sz{original VG?} names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure*}

>>>>

@@

\begin{figure*}[htp]
	\centering
	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN_v2.png}
% WAS:	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
% But it's not really a cumulative histogram
	\caption{Number of images per domain ManyNames. Colors are the original VG names; all high-frequency names are shown, as well as a few lower-frequency names.}
	\label{fig:overview_dataset1}
\end{figure*}
